---
title: "CASE Study 10"
author: "Gideon Miles"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package

library(tidyverse)
library(dygraphs)
library(tidyverse)
library(tidyquant)
library(quantmod)

```

```{r load_data}
# Use this R-Chunk to import all your datasets!

```

## Background

Your data science income has ballooned, and you need to find somewhere to invest $25,000 that you have saved over the last year. You have a savvy investment friend that is kind enough to tell you ten stocks he has been watching during the last year. You will need to visualize the last five years performance to help in the conversation with your friend.

Your friend is going to give you his tickers at the beginning of your half-hour meeting with him (he is a busy friend). You will need to build an .Rmd file that will build a suite of visualizations rapidly for your conversation. You will need a series of stock performance graphics using library(dygraphs) and library(ggplot2). In real life, you might use one or the other, but this task is built to help you move from ts and xts to tidy objects for visualization.

Specifically, in class the Tuesday following this case study you will get 5 - 10 ticker symbols and will need to build visualizations quickly that allows you to answer questions about the stocks in a few seconds.



## Data Wrangling

```{r}
s1<- readline(prompt="Enter Stock 1: ")
s2<- readline(prompt="Enter Stock 2: ")
s3<- readline(prompt="Enter Stock 3: ")
s4<- readline(prompt="Enter Stock 4: ")
s5<- readline(prompt="Enter Stock 5: ")
s6<- readline(prompt="Enter Stock 6: ")
s7<- readline(prompt="Enter Stock 7: ")
s8<- readline(prompt="Enter Stock 8: ")
s9<- readline(prompt="Enter Stock 9: ")
s10<- readline(prompt="Enter Stock 10: ")

Stocks<-c(s1,s2,s3,s4,s5,s6,s7,s8,s9,s10)
```


```{r}
function(input, output, session) {

  output$urlText <- renderText({
    as.character(input$my_url)
  })

  observe({
    # Run whenever reset button is pressed
    input$reset

    # Send an update to my_url, resetting its value
    updateUrlInput(session, "my_url", value = "http://www.r-project.org/")
  })
}
```


```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!




##Stocks<-c("CXW", "F", "GM", "KR", "WDC", "NKE","T", "WDAY", "WFC", "WMT")


SStocks <- tq_get(Stocks, get = "stock.prices", from = "2015-05-05", to = "2020-11-21")


#pivot_wider
#convert to xts
#
#ggplot looking at the Volume.  Just add it to the plot

#SStocks %>% group_by(symbol) %>% 
#for(i in Stocks){
  
#print(i)
  
#}

#?pivot+wider()
  
wide <- SStocks %>% select(symbol, date, adjusted)

SStocks2<-wide %>%   pivot_wider(names_from=symbol, id_cols=date, values_from=adjusted ) 

SStocks2<-SStocks2 %>% timetk::tk_xts(date=date)


# price at each date.

dygraph(data=SStocks2, main="Test Main")


```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!

dygraph(data=Kro2$Test, main="Test Main")

```

```

## Conclusions
