---
title: "Task 18"
author: "Gideon Miles"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(tidyquant)
library(quantmod)

```

```{r load_data}
# Use this R-Chunk to import all your datasets!

#[ ] Take notes on your reading of the new R package in the README.md or in a ‘.R’ script in the class task folder
#[ ] List the three stocks that your friend picks and the three that you pick
#[ ] Pull the price performance data using library(tidyquant) or library(quantmod)
#[ ] Build a visualization that shows who is winning each day of the competition
#[ ] In the previous visualization or with another visualization show which stock is helping the winner of the competition
#[ ] Create an .Rmd file with 1-2 paragraphs summarizing your graphics and the choices you made in the data presentation
#[ ] Compile your .md and .html file into your git repository



```

## Background

The stock market is overflowing with data. There are many packages in R that allow us to get quick access to information on publicly traded companies. Imagine that you and a friend each purchased about $1,000 of stock in three different stocks at the start of October last year, and you want to compare your performance up to this week. Use the stock shares purchased and share prices to demonstrate how each of you fared over the period you were competing (assuming that you did not change your allocations).

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
tq_index_options()
DOW<-tq_index("DOW")
DOWG<-tq_index("DOWGLOBAL")
SP600<-tq_index("SP600")

NASDAQ<-tq_exchange("NASDAQ")

CP<-NASDAQ %>% filter(symbol=="PRSS")

APPL<-NASDAQ %>% filter(symbol=="AAPL")

aapl_prices  <- tq_get("AAPL", get = "stock.prices", from = " 2000-01-01")

df2 <- tq_get(c("ATVI", "AMD", "DELL", "ALGN", "ALLT", "GOOG"), get = "stock.prices", from = "2017-10-01", to = "2020-10-01")


wide <- df2 %>% select(symbol, date, adjusted)

wide %>%   pivot_wider(names_from=symbol, id_cols=date, values_from=wide[,2:7] ) 



                
#Steve Jobs Death- Octob 5th 2011
```

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!
library(utils)

ggplot(data=wide)+geom_line(aes(x=date,y=adjusted,color=symbol))+
  geom_text(data=subset(wide, date=date(2020-09-30)), aes(label=symbol, x=date, color=symbol, y=adjusted))





p = ggplot(temp.dat) + 
  geom_line(aes(x = Year, y = Capex, group = State, colour = State)) + 
  geom_text(data = subset(temp.dat, Year == "2014"), aes(label = State, colour = State, x = Inf, y = Capex), hjust = -.1) +
  scale_colour_discrete(guide = 'none')  +    
  theme(plot.margin = unit(c(1,3,1,1), "lines")) 

p
```

## Conclusions
