---
title: "Task 25"
author: "Gideon Miles"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(sf)
library(USAboundaries)
library(leaflet)




```

```{r load_data}
# Use this R-Chunk to import all your datasets!
cap<-read_csv("statecapitals.csv")


```

## Background

_Place Task Background Here_

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!
library(maps)
library(USAboundaries)
library(tidyverse)
library(leaflet)

USALat<-world.cities %>% filter(country.etc=="USA")



USA2<-us_cities()

cities <- USA2 %>% filter(state_name!="Alaska", state_name!="Hawaii") %>% group_by(state_name) %>%  top_n(3, population) %>% mutate(top3=row_number(desc(population))) %>% mutate(long = map_dbl(geometry, ~st_centroid(.x)[[1]]),
         lat = map_dbl(geometry, ~st_centroid(.x)[[2]]))


```

## Data Visualization

#### Top Three Cities By Population in Each of the Continential 48 States

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!

leaflet() %>% addTiles() %>% 
  addMarkers(data = cities,
             lng = ~long,
             lat = ~lat,
             label = ~paste(name_2010, "Population:", population),
             clusterOptions = markerClusterOptions())
```

## Conclusions

I Love leafelt.  There is just something about an interactive graph that make sit feel like you've accomplsihed something more.  Something more insighful, intuitive, and feel like you have control over the sights you ar looking for.  It feels like you can play with and explore reality as you choose more fully rather than simiply being given a display, even if it is no different in the fact that the data given you is the same.  
