---
title: "Case Study 4"
author: "Gideon Miles"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(downloader)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!


bob<-tempfile()

  download("https://byuistats.github.io/M335/data/heights/Height.xlsx", bob, mode="wb")

d1<-readxl::read_xlsx(bob, skip=2)

#colnames(d1) <- d1[2, ]       #assign 1st row to column name


#could i just rotate one colum to be a vector?

d3<-pivot_longer(d1, cols = "1800":"2011", names_to="Year", values_to="Average_Height")
d3<-na.omit(d3)

```

## Background

_Place Task Background Here_

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!

```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!
  library(ggbeeswarm)

ggplot(data=d3, mapping=aes(x=Year, y=Average_Height, color="red"))

  ggplot(d3, aes(x=Year, y=Average_Height)) + stat_summary(fun="mean", geom="bar")+
     geom_quasirandom(aes(color=Year, alpha=0))+
  ylab("Height on Average")+
  ggtitle("Are We Getting Taller?")+
    stat_smooth(method="lm", se=FALSE)
  
  
  d3<-d3 %>% rename(Location='Continent, Region, Country')

  
  d4<-filter(d3, Location=="Germany")
 
  ##oor could i just scale it by decade?
  

  
#+geom_bar(stat="count", inherit.aes=TRUE )


  ggplot(data=d4, mapping=aes(x=Year, y=Average_Height, color="red"))

  ggplot(d4, aes(x=as.numeric(Year), y=Average_Height)) + geom_line(color="blue")+
    ggtitle("Height Increase In Germany", sub="By Decade")+
    xlab("Year")+
    ylab("Height")

  
  
```

Okay So I Dont Need The First Point But I liked it so I included it.  The Second Vizualization is the one for the class much more boring.


## Part 2

```{r}
https://byuistats.github.io/M335/data/heights/germanconscr.dta
## German
library(readxl)
library(foreign)
library(haven)

GermCon<- read.dta("germanconscr.dta")




GermPris<-read.dta("germanprison.dta")

##Bavarian

bob<-tempfile()
Bavar <- download("https://byuistats.github.io/M335/data/heights/germanprison.dta?raw=true", destfile= bob, mode="wb")

b19<-read.dta(bob)
b19<-b19 %>% rename(Height_IN=height)
b19<-b19 %>% rename(Birth_Year = bdec)
b19<-b19 %>% mutate(Study="b19")
b19<-b19 %>% select(Study, Height_IN, Birth_Year)


## West Germany  ## get this imported.
bob<-tempfile()
  bob_dir<-tempdir()

  bob1<-tempfile()
  
#download.file("https://byuistats.github.io/M335/data/heights/Heights_south-east.zip", destfile=bob1, mode= "wb")

#unzip(bob1,exdir=bob_dir)
#WestGem<-read.dbf(paste(bob_dir, "WestGermany.dbf", sep="\\"))


temp <- tempfile()
download("https://byuistats.github.io/M335/data/heights/Heights_south-east.zip?raw=true", temp, mode = "wb")

unzip(temp) 
dbf <- read.dbf("B6090.DBF", as.is = F)

dbf<-dbf %>% rename("Year"=SJ)
g18<-dbf %>% mutate(as.numeric(Height_IN=CMETER/2.54))
g18<-g18 %>% mutate(Study="g18")
g18<-g18 %>% select(Study, Height_IN, Year)

#cmeter is centemeter
#convert that to inches
#mutate those variables
#select only inches and Birth Year, and study name and save them into a new variable called ___




## Bureau of labor stats
bob<-tempfile()
download.file("https://github.com/hadley/r4ds/raw/master/data/heights.csv",destfile=bob,mode= "wb")
Bureau<-read.csv(bob)


## Wisconsin
Wisconsin<-download("http://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav", destfile=bob, mode= "wb")

bob<-tempfile()
download.file("http://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav?raw=true",destfile=bob,mode= "wb")
Wisconsin<-read_sav(bob)

w20<-Wisconsin %>% select(DOBY, DOBM, RT216F,RT216I) #f  #i
w20<-w20 %>% rename(DOBY)
w20<-w20 %>% mutate(Birth_Year= paste0("19", w20$DOBY))
w20<-w20 %>% mutate(Height_IN=as.numeric((RT216F*12)+RT216I))
w20<-w20 %>% filter(Height_IN>=0)
w20<-mutate(w20, Study="w20")
w20<-w20 %>% select(Birth_Year,Height_IN, Study)



b19<-select(birth_year, height.in, height.cm, Bavar)



g18<-GermCon %>% select(bdec, height, height)
g18<-mutate(g18, Study="g18")
g18<-mutate(g18, Height_CM= height*2.54)
g18<-g18 %>% rename(Height_IN=height)
g18<-g18 %>% rename(Birth_Year=bdec)
g18<-g18 %>% select(Birth_Year,Height_IN, Study)

g19<-GermPris %>% select(bdec, height, height)
g19<-mutate(g19, Study="g19")
g19<-mutate(g19, Height_CM= height*2.54)
g19<-g19 %>% rename(Height_IN=height)
g19<-g19 %>% rename(Birth_Year=bdec)
g19<-g19 %>% select(Birth_Year,Height_IN, Study)


us20<-Bureau %>% rename(Height_IN=height)
us20<-us20 %>% mutate(Study="us20")
us20<-us20 %>% mutate(Birth_Year=1950)
us20<-us20 %>% select(Birth_Year,Height_IN, Study)





alld <- rbind(b19, g18, g19, us20, w20)

ggplot(alld)+
  geom_point()+
  facet(~Study)


#Use the following code to combine your five individual dataset into one dataset
#alld <- bind_rows(b19, g18, g19, us20, w20)
#[ ] Make a small-multiples plot of the five studies containing individual heights to examine the question of height distribution across centuries




#The plan
#Filter Each Data set down to the bare bones I need, then create a new dataset by grouping them by the old data set
#Will a combining know to well i can just add a coloum that just has the name, yeah that works.



```



```{r}

```


## Conclusions

We Are Increasing in Height, Germans on average in the last 200 years have increased a net height of 10 inches in the last 200 years, that about ab inch a decade.  Which is interesting.
