---
title: "Task 10"
author: "Gideo Miles"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)
library(mosaic)
library(directlabels)
```

```{r load_data}
# Use this R-Chunk to import all your datasets!
hap<-read_csv("happiness-cantril-ladder.csv")


```

## Background

_Place Task Background Here_

## Data Wrangling

```{r tidy_data}
# Use this R-Chunk to clean & wrangle your data!

hap<-hap %>% rename(country=Entity)
hap<-hap %>% rename(year=Year)
hap<-hap %>% rename(happiness="Life satisfaction in Cantril Ladder (World Happiness Report 2019)")


hap %>% filter(country %in% c("Norway", "Australia", "Germany", "Colombia", "Bolivia", "Bhutan")) %>% 
ggplot(mapping=aes(x=year,y=happiness, color=country))+
  geom_line()+
  geom_point()+
  coord_cartesian(ylim=c(0,10), xlim=c(2005,2018))+
  theme_minimal()+
  theme(axis.title.x=element_blank(),
        panel.grid.major.x=element_blank(),
        panel.grid.minor.x=element_blank(),
        panel.grid.minor.y=element_blank(),
        panel.grid.major.y=element_line(linetype="dashed", color="dark gray"),
        legend.position="none",
        plot.caption= element_text(hjust=0),
        plot.title.position="plot")+
  scale_y_continuous(breaks=seq(0,10, by =2),
                   labels=paste(seq(0,10, by=2), "", sep=""))  +
                     scale_x_continuous(breaks=c(2005,seq(2006,2018, by=2)),
                                        expand=expand_scale(mult=c(.05,.15)))+
                     geom_dl(aes(label=country),method=list(dl.trans(x=x+2),
                                                    "last.points"))+
                     labs(title="Self reported life satisfaction, 2015-2018",
                          subtitle="superlongsubtitle \nkeeps on going and going",
                          caption="Source:World Happiness Report")
             
```

## Data Visualization

```{r plot_data}
# Use this R-Chunk to plot & visualize your data!
library(ourworldindata)

h<-financing_healthcare


h<-h %>% filter(country !="Abkhazia")

ggplot(data = h, aes(x = year, y = child_mort, color = continent)) +
 theme_bw() +
  scale_y_continuous(trans = "sqrt")+
  geom_point() +
geom_smooth(color="black")+
  ggtitle("Child Mortality", subtitle = "Over Time From 1750- 2000") +
  labs(y="Child Mortality", x="Year", color="Continents")+
   facet_grid(~continent) 

  



```

## Conclusions

We see above that the Child Mortality Rate Drops shaprly in every country in about 1800.  I havent found a reasons as to the drop in Mortality Rate.  It would be interesting to compare this to birth rates.  If people simiple started having less children.  There has been a correlation found between lower morality rates and less children.  Im sure there are other factors that tie into that, however there seems to be a tie there.  I would posit that there are some significant additional causes for the drop off, for example 

One Case sighted an increase in secularism as a potential cause, of man seeking to take a greater hold of his own fate his own wellbeing rather.  Rather I would say more or people taking an interest in medicine rather than caring less about God.  Once they realized they could also use medicine.  

Regardless around 1850 every continent inthe world saw the start of a drastic decline of the next 50 years to bottoming out.   